---
title: "Maternal Dashboard"
output: 
 flexdashboard::flex_dashboard:
   orientation: rows
   vertical_layout: fill
   source_code: embed
runtime: shiny
---

```{r setup, include=FALSE}
library(flexdashboard)
library(dplyr)
library(tidyverse)
library(shiny)
library(ggplot2)
library(plotly)
library(knitr)
library(lubridate)
library(scales)
library(readxl)

theme_set(theme_bw())
```

```{r mockdata, eval = T}
# change to eval = F here and T below to use excel file

set.seed(42)
SiteName = c("A","B","C","D","E")
date = rep(c("1/1/2018","2/1/2018","3/1/2018","4/1/2018","5/1/2018",
             "6/1/2018","7/1/2018","8/1/2018","9/1/2018","10/1/2018","11/1/2018","12/1/2018"),
           each = 5) %>% as.tibble
dates<-as.POSIXct(date$value,format = "%m/%d/%Y") %>% as.tibble # change character to date format

maternal = as.data.frame(cbind(SiteName, dates)) # make maternal
maternal$SiteName <- as.character(maternal$SiteName) # change data type
maternal<-rename(maternal, Period = value)

maternal$PreM1Data_DEN = rep(floor(runif(12,100,500)), 5)
maternal$PreM1Data_NUM = floor(maternal$PreM1Data_DEN*(runif(60,.45,.65)))
maternal$PreM2Data_DEN = maternal$PreM1Data_NUM
maternal$PreM2Data_NUM = ceiling(maternal$PreM2Data_DEN *(runif(60,.05,.15)))
maternal$PreM3Data_NUM = ceiling(maternal$PreM2Data_NUM *(runif(60,.9,1)))
maternal$PreM3Data_DEN = maternal$PreM2Data_NUM

maternal$PostM1Data_DEN = rep(floor(runif(12,50,400)), 5)
maternal$PostM1Data_NUM = floor(maternal$PostM1Data_DEN*(runif(60,.45,.65)))
maternal$PostM2Data_NUM = ceiling(maternal$PostM1Data_NUM*(runif(60,.05,.15)))
maternal$PostM2Data_DEN = maternal$PostM1Data_NUM
maternal$PostM3Data_NUM = ceiling(maternal$PostM2Data_NUM*(runif(60,.9,1)))
maternal$PostM3Data_DEN = maternal$PostM2Data_NUM

###

agg_maternal <- maternal %>% select(-c(SiteName)) %>%  #select(-c(SiteName, HospitalName, New)) 
                                       group_by(Period) %>% summarise_all(sum, na.rm = T) # don't sum with NA's  
attach(agg_maternal)
agg_maternal$PrePostNums <- PreM1Data_NUM + PostM1Data_NUM 
agg_maternal$PrenatalPctScreened <- PreM1Data_NUM/PreM1Data_DEN 
agg_maternal$PrenatalPctPos <- PreM2Data_NUM/PreM2Data_DEN 
agg_maternal$PrenatalPctConnected <- PreM3Data_NUM/PreM3Data_DEN 
agg_maternal$PostPctScreened <- PostM1Data_NUM/PostM1Data_DEN 
agg_maternal$PostPctPos <- PostM2Data_NUM/PostM2Data_DEN 
agg_maternal$PostPctConnected <- PostM3Data_NUM/PostM3Data_DEN 

attach(maternal)
maternal$PrePostNums <- PreM1Data_NUM + PostM1Data_NUM 
maternal$PrenatalPctScreened <- PreM1Data_NUM/PreM1Data_DEN 
maternal$PrenatalPctPos <- PreM2Data_NUM/PreM2Data_DEN 
maternal$PrenatalPctConnected <- PreM3Data_NUM/PreM3Data_DEN 
maternal$PostPctScreened <- PostM1Data_NUM/PostM1Data_DEN 
maternal$PostPctPos <- PostM2Data_NUM/PostM2Data_DEN 
maternal$PostPctConnected <- PostM3Data_NUM/PostM3Data_DEN

```

```{r realdata, eval = F}
# change to eval = F above and T here to use excel file

maternal <- read_excel("~/file.xls")

"/" <- function(x,y) ifelse(y==0,0,base:::"/"(x,y)) # redefine division by zero so there's no NaN's produced

agg_maternal <- maternal %>% select(-c(SiteName, HospitalName, New)) %>%  
                                       group_by(Period) %>% summarise_all(sum, na.rm = T)  # ignore NA's

attach(agg_maternal)
agg_maternal$PrePostNums <- PreM1Data_NUM + PostM1Data_NUM
agg_maternal$PrenatalPctScreened <- PreM1Data_NUM/PreM1Data_DEN
agg_maternal$PrenatalPctPos <- PreM2Data_NUM/PreM2Data_DEN
agg_maternal$PrenatalPctConnected <- PreM3Data_NUM/PreM3Data_DEN
agg_maternal$PostPctScreened <- PostM1Data_NUM/PostM1Data_DEN
agg_maternal$PostPctPos <- PostM2Data_NUM/PostM2Data_DEN
agg_maternal$PostPctConnected <- PostM3Data_NUM/PostM3Data_DEN

attach(maternal)
maternal$PrePostNums <- PreM1Data_NUM + PostM1Data_NUM
maternal$PrenatalPctScreened <- PreM1Data_NUM/PreM1Data_DEN
maternal$PrenatalPctPos <- PreM2Data_NUM/PreM2Data_DEN
maternal$PrenatalPctConnected <- PreM3Data_NUM/PreM3Data_DEN
maternal$PostPctScreened <- PostM1Data_NUM/PostM1Data_DEN
maternal$PostPctPos <- PostM2Data_NUM/PostM2Data_DEN
maternal$PostPctConnected <- PostM3Data_NUM/PostM3Data_DEN
```

Screening by SiteName {data-navmenu="Choose a view"}
=====================================

Column {.sidebar}
-----------------------------------------------------------------------

```{r widget1}

h3("Screening by site")

h5("There are three different options to view this comparison")

hr()
min_date <-as.Date(min(Period)) # create min and max for slider
max_date <- as.Date(max(Period))

sliderInput("Date_range_selector0", "Date Range: ", min = min_date, max =max_date, value=as.Date(c("2018-01-01","2018-12-01")),timeFormat="%b %Y") # date slider

# each has a different title "Date_range_selectorN" ... be sure to change

# select each SiteName with drop down menus
hr()

agg_select <- agg_maternal %>%  select(Period, PrenatalPctPos) %>% mutate(SiteName = "average") # option to show average line
maternal_avg <- full_join(agg_select, maternal)

which_SiteName <- maternal_avg %>% distinct(SiteName) %>% pull %>% as.character() %>% sort()

selectInput("SiteName_choice1", label = ("Select Site 1"),
           choices = which_SiteName, selected = NULL)
selectInput("SiteName_choice2", label = ("Select Site 2"),
           choices = which_SiteName, selected = NULL)
selectInput("SiteName_choice3", label = ("Select Site 3"),
           choices = which_SiteName, selected = NULL)
selectInput("SiteName_choice4", label = ("Select Site 4"),
           choices = which_SiteName, selected = NULL)

```

Row 1
-----------------------------------------------------------------------

### plot 1
```{r, eval = T}
renderPlotly({                                                        # render the interactive plot
 # create a ggplot and make interactive by calling ggplotly

p<- maternal_avg %>% filter(SiteName %in% input$SiteName_choice1& 
                              between(as.Date(Period),
                                      input$Date_range_selector0[1], 
                                      input$Date_range_selector0[2])) %>% # filters only the SiteName the user chose
  #filter(Period %in% input$daterange) %>% 
  ggplot(aes(x=Period, y=PrenatalPctPos, group= 1,                   # group = 1 to plot since each month has 1 data point
              text = paste('SiteName: ', SiteName, "",            # create tooltip text
                           'proportion positive: ', round(PrenatalPctPos,3)))) +
     geom_line(aes(x=Period, y=PrenatalPctPos),color = "red") +       # each panel has its own color
     geom_point() +                                                   # show the points
     geom_hline(yintercept=0.12, linetype="dashed", color = "black") + # horizontal reference line
     annotate(geom="text", label="12% PRAMS", x = as.POSIXct('2018-02-01'), y=.125, vjust=-1) + # annotate the line
     xlab("Month") + # x and y labels
     ylab("Proportion")  +
  scale_x_datetime(date_breaks = "1 month", labels = date_format("%b %Y")) + # format x axis
  theme(axis.text.x  = element_text(angle=45, vjust=0.5)) # x labels at 45 deg angle
ggplotly(p, tooltip = ("text"))
 })
```

```{r, eval = F}
# syntax for plotly
renderPlotly({

maternal_avg %>% filter(SiteName %in% input$SiteName_choice1& 
                              between(as.Date(Period),
                                      input$Date_range_selector0[1], 
                                      input$Date_range_selector0[2])) %>% # filters only the SiteName the user chose
   plot_ly(x = ~Period, y = ~PrenatalPctPos
         , color = I('red')                        # set color of line
         , type = "scatter", mode = "lines+markers"# line plot with dot markers
         , alpha = 0.5                             # transparency control
         , hoverinfo = 'text'                      # set hover text
         , text = ~paste("SiteName: ", SiteName, '\nproportion: ', round(PrenatalPctPos,3))
           ) %>% 
   add_lines(x=c(0,12), y=c(.12,.12)               # create gray reference line
             , color = I('gray')
             , hoverinfo = 'text'                  # hover text
             , text = ~paste("12% PRAMS")) %>% 
             layout(showlegend = F) %>%            # no legend 
   layout(xaxis=list(title = "month")              # set axis titles
          , yaxis=list(title = "proportion"))
 })
```

### plot 2

```{r}
renderPlotly({
p2<-maternal_avg %>% filter(SiteName %in% input$SiteName_choice2& 
                              between(as.Date(Period),
                                      input$Date_range_selector0[1], 
                                      input$Date_range_selector0[2])) %>%
 ggplot(aes(x=Period, y=PrenatalPctPos, group= 1, 
              text = paste('SiteName: ', SiteName, "",
                           'proportion positive: ', round(PrenatalPctPos,3)))) +
     geom_line(aes(x=Period, y=PrenatalPctPos),color = "blue") +
     geom_point() +
     geom_hline(yintercept=0.12, linetype="dashed", color = "black") + 
     xlab("Month")+
     ylab("Proportion")  +
  scale_x_datetime(date_breaks = "1 month", labels = date_format("%b %Y")) + 
  theme(axis.text.x  = element_text(angle=45, vjust=0.5))
ggplotly(p2, tooltip = c("text"))
 })
```

Row 2
-----------------------------------------------------------------------
### plot 3
```{r}
renderPlotly({
p3<-maternal_avg %>% filter(SiteName %in% input$SiteName_choice3 & 
                              between(as.Date(Period),
                                      input$Date_range_selector0[1], 
                                      input$Date_range_selector0[2])) %>%
   ggplot(aes(x=Period, y=PrenatalPctPos, group= 1, 
              text = paste('SiteName: ', SiteName, "",
                           'proportion positive: ', round(PrenatalPctPos,3)))) +
     geom_line(aes(x=Period, y=PrenatalPctPos),color = "dark green") +
     geom_point() +
     geom_hline(yintercept=0.12, linetype="dashed", color = "black") + 
     xlab("Month")+
     ylab("Proportion")  +
  scale_x_datetime(date_breaks = "1 month", labels = date_format("%b %Y")) + 
  theme(axis.text.x  = element_text(angle=45, vjust=0.5))
ggplotly(p3, tooltip = c("text"))
})
```

### plot 4
```{r}
renderPlotly({
p4<-maternal_avg %>% filter(SiteName %in% input$SiteName_choice4& 
                              between(as.Date(Period),
                                      input$Date_range_selector0[1], 
                                      input$Date_range_selector0[2])) %>%
   ggplot(aes(x=Period, y=PrenatalPctPos, group= 1,    
              text = paste('SiteName: ', SiteName, "",
                           'proportion positive: ', round(PrenatalPctPos,3)))) +
     geom_line(aes(x=Period, y=PrenatalPctPos),color = "purple") +
     geom_point() +
     geom_hline(yintercept=0.12, linetype="dashed", color = "black") + 
     xlab("Month")+
     ylab("Proportion")  +
  scale_x_datetime(date_breaks = "1 month", labels = date_format("%b %Y")) + 
  theme(axis.text.x  = element_text(angle=45, vjust=0.5))
ggplotly(p4, tooltip = c("text"))
})
```


Screening by SiteName option deux {data-navmenu="Choose a view"}
=====================================

Column {.sidebar}
-----------------------------------------------------------------------

```{r, eval = T}
h3("Screening by site")

h5("There are three different options to view this comparison")

hr()
min_date <-as.Date(min(Period)) # create min and max for slider
max_date <- as.Date(max(Period))

sliderInput("Date_range_selector", "Date Range: ", min = min_date, max =max_date, value=as.Date(c("2018-01-01","2018-12-01")),timeFormat="%b %Y") # date slider

# each has a different title "Date_range_selectorN" ... be sure to change

# select each SiteName with check boxes
hr()
agg_select <- agg_maternal %>%  select(Period, PrenatalPctPos) %>% mutate(SiteName = "average") # option to show average line
maternal_avg <- full_join(agg_select, maternal)

which_SiteName <- maternal_avg %>% distinct(SiteName) %>% pull %>% as.character() %>% sort() 

checkboxGroupInput("SiteName_choice", label = h3("Select Site"),
           choices = which_SiteName, selected = "average", inline = T)
```

Column
---------

###

```{r, eval = T}
renderPlotly({
p4<-maternal_avg %>% filter(SiteName %in% input$SiteName_choice& 
                              between(as.Date(Period),
                                      input$Date_range_selector[1], 
                                      input$Date_range_selector[2])) %>% # filter SiteName based on user input
  # each has a different title "Date_range_selectorN" ... be sure to change
   ggplot(aes(x = Period, y = PrenatalPctPos, group = SiteName,    
              text = paste('SiteName: ', SiteName, "", # create tooltip
                           'proportion positive: ', round(PrenatalPctPos,3), "",
                           'month: ', paste(month(Period, label = TRUE),year(Period))))) +
     geom_point(aes(x=Period, y=PrenatalPctPos,color = SiteName)) + # make points
     geom_line(aes(x=Period, y=PrenatalPctPos,color = SiteName)) + # each SiteName has own line
     geom_hline(yintercept=0.12, linetype="dashed", color = "black") + # reference line
     annotate(geom="text", label="12% PRAMS", x = as.POSIXct('2018-02-01'), y=.121, vjust=-1) + # annotate reference line
     xlab("Month")+ # axis labels
     ylab("Proportion") +
  scale_x_datetime(date_breaks = "1 month", labels = date_format("%b %Y"))+ # format x axis
  theme(axis.text.x  = element_text(angle=45, vjust=0.5)) # x labels at 45 deg angle

ggplotly(p4, tooltip = c("text"))
})
```


Screening by SiteName option tres {data-navmenu="Choose a view" data-orientation=columns}
=====================================

Column 1 {.sidebar}
--------

```{r}

h3("Screening by site")

h5("There are three different options to view this comparison")

hr()

min_date <-as.Date(min(Period)) # create min and max for slider
max_date <- as.Date(max(Period))

sliderInput("Date_range_selector2", "Date Range: ", min = min_date, max =max_date, value=as.Date(c("2018-01-01","2018-12-01")),timeFormat="%b %Y") # date slider
# each has a different title "Date_range_selectorN" ... be sure to change

hr()                

agg_select <- agg_maternal %>%  select(Period, PrenatalPctPos) %>% mutate(SiteName = "average") # option to show average line
maternal_avg <- full_join(agg_select, maternal)

which_SiteName <- maternal_avg %>% distinct(SiteName) %>% pull %>% as.character() %>% sort() 


selectInput("SiteName_choice5", label = ("Select Site Name"),
           choices = which_SiteName, selected = "average", multiple = T)
```

Column 2
--------

###

```{r}
renderPlotly({
p4<-maternal_avg %>% filter(SiteName %in% input$SiteName_choice5 & 
                              between(as.Date(Period),
                                      input$Date_range_selector2[1], 
                                      input$Date_range_selector2[2])) %>% # filter based on user input
  # each has a different title "Date_range_selectorN" ... be sure to change
   ggplot(aes(x=Period, y=PrenatalPctPos, group= SiteName,    
              text = paste('SiteName: ', SiteName, "", # tooltip
                           'proportion positive: ', round(PrenatalPctPos,3), "",
                           'month: ', paste(month(Period, label = TRUE),year(Period))))) +
     geom_line(aes(x=Period, y=PrenatalPctPos,color = SiteName)) +
     facet_grid(SiteName~., shrink = F) + # each SiteName in own grid
     geom_point() + # make points (black since not coloring by SiteName)
     geom_hline(yintercept=0.12, linetype="dashed", color = "black")+ # reference line
     annotate(geom="text", label="12% PRAMS", x = as.POSIXct('2018-02-01'), y=.121, vjust=-1) + # reference line text
     xlab("Month")+ # axis labels
     ylab("Proportion")  +
  scale_x_datetime(date_breaks = "1 month", labels = date_format("%b %Y")) + # format x axis
  theme(axis.text.x  = element_text(angle=45, vjust=0.5)) # x labels at 45 deg angle
ggplotly(p4, tooltip = c("text"))
})
```

Number and % Screened {data-navmenu="Choose a view" data-orientation=rows}
=====================================

## Column {.sidebar}

Can describe page here, or include more control widgets

```{r}
hr()
min_date <-as.Date(min(Period)) # create min and max for slider
max_date <- as.Date(max(Period))

sliderInput("Date_range_selector3", "Date Range: ", min = min_date, max =max_date, value=as.Date(c("2018-01-01","2018-12-01")),timeFormat="%b %Y") # date slider
# each has a different title "Date_range_selectorN" ... be sure to change

hr()
```


## Row {data-height=950}

### Number of women screened for depression (pre and post)
```{r}
renderPlotly({
p<-agg_maternal %>% filter(between(as.Date(Period),
                                      input$Date_range_selector3[1], 
                                      input$Date_range_selector3[2])) %>%
  # each has a different title "Date_range_selectorN" ... be sure to change
  ggplot(., aes(Period, 
                            PrePostNums , 
                            group = 1, # 1 data point per month
                            text = paste("number screened: ", # tooltip
                                   PrePostNums, "",
                                  'month: ', paste(month(Period, label = TRUE),year(Period))))) + 
  geom_line(stat = "summary") + # plot lines
  geom_point(alpha = .5) +
  xlab("Month") + # axis labels
  ylab("Total prenatal and postpartum screening") +
  ggtitle("Number of women screened for depression (pre and post)") + # plot title
  scale_x_datetime(date_breaks = "1 month", labels = date_format("%b %Y")) + # format x axis
  theme(axis.text.x  = element_text(angle=45, vjust=0.5))

ggplotly(p, tooltip= c("text"))
})
```

### Prenatal and postpartum depression screening
```{r}
renderPlotly({
p<-select(agg_maternal, c("PrenatalPctScreened", "PostPctScreened", "Period")) %>% # select only data of interest
  rename(., Prenatal = PrenatalPctScreened , Postpartum = PostPctScreened) %>% # rename variables
  gather(., key = timepoint, value = measure, "Prenatal", "Postpartum") %>% # reshape to plot
  filter(between(as.Date(Period),
                                      input$Date_range_selector3[1], 
                                      input$Date_range_selector3[2])) %>%
  ggplot(., aes(y = measure, x = Period, 
              color = timepoint, # plot each timepoint a different color and line
              group = timepoint, 
              text = paste(round(measure,3)*100,"% screened", # tooltip text
                           "",timepoint,
                           "",
                           'month: ', paste(month(Period, label = TRUE),year(Period))))) +  
  xlab("Month") + # axis labels
  ylab("Proportion Screened") +
  geom_line(stat = "summary") + # plot line
  geom_point(alpha = .5) + # set transparency of points
  ggtitle("Prenatal and postpartum depression screening") + # plot title
  geom_hline(yintercept=1, linetype="dashed", color = "black") + # reference line
  annotate(geom="text", label="target 100%", x = as.POSIXct('2018-03-01'), y=.98, vjust=-1) + # label reference line
  scale_x_datetime(date_breaks = "1 month", labels = date_format("%b %Y")) + # format x axis
  theme(axis.text.x  = element_text(angle=45, vjust=0.5)) +
  labs(color = "") # remove legend title 

ggplotly(p, tooltip = "text")
})
```

## Screened, tables {.tabset .tabset-fade}

### Women screened at their first prenatal visit
```{r}
# reshape data to make table of data of interest
Z<-select(maternal, c("SiteName","PreM1Data_NUM","PreM1Data_DEN", "Period")) %>%
  group_by(Period) %>% 
  filter(!is.na(PreM1Data_NUM)) %>% # don't sum over NA
  summarise("prenatal screen" = sum(PreM1Data_NUM) , # name of each row
            "denom" = sum(PreM1Data_DEN), 
            `n SiteName` = n()) 
new<-t(Z) # transpose df
Z$Period <- paste(month(Z$Period, label = TRUE),year(Z$Period)) %>% as.character() # column names 
colnames(new) <- Z$Period
new[-1,] %>% knitr::kable(caption = "Women screened at their first prenatal visit") # pretty table with title
```

### Women screened at their postpartum visit
```{r}
Z<-select(maternal, c("SiteName","PostM1Data_NUM","PostM1Data_DEN", "Period")) %>% 
  group_by(Period) %>% 
  filter(!is.na(PostM1Data_NUM)) %>% # don't sum over NA
  summarise("postpartum screen" = sum(PostM1Data_NUM), # name of each row
            "denom" = sum(PostM1Data_DEN),
            `n SiteName` = n()) 
new<-t(Z) # transpose df
Z$Period <- paste(month(Z$Period, label = TRUE),year(Z$Period)) %>% as.character() # column names
colnames(new) <-Z$Period
new[-1,] %>% knitr::kable(caption = "Women screened at their postpartum visit") # pretty table with title
```


Prenatal screening rates {data-navmenu="Choose a view"}
=====================================

## Column {.sidebar}

Can describe page here, or include more control widgets

```{r}
hr()
min_date <-as.Date(min(Period)) # create min and max for slider
max_date <- as.Date(max(Period))

sliderInput("Date_range_selector4", "Date Range: ", min = min_date, max =max_date, value=as.Date(c("2018-01-01","2018-12-01")),timeFormat="%b %Y") # date slider
# each has a different title "Date_range_selectorN" ... be sure to change

hr()
```


## Graph
### Prenatal depression screening
```{r}
renderPlotly({
p<-agg_maternal %>% filter(between(as.Date(Period),
                                      input$Date_range_selector4[1], 
                                      input$Date_range_selector4[2])) %>% 
  # each has a different title "Date_range_selectorN" ... be sure to change
  ggplot(., aes(Period, PrenatalPctScreened, group = 1, label = PrenatalPctScreened )) + 
  geom_line(stat = "summary") + # plot line
  geom_point() + # points black since not coloring by data
  geom_text(aes(label=round(PrenatalPctScreened ,3)), nudge_y = .01) + # set label for points
  xlab("Month") + # axis titles
  ylab("Proportion Screened") +
  ggtitle("Prenatal depression screening") + # plot title
  geom_hline(yintercept=1, linetype="dashed", color = "black") + # reference line and text
  annotate(geom="text", label="target 100%", x = as.POSIXct('2018-02-01'), y=.99, vjust=-1) +
  scale_x_datetime(date_breaks = "1 month", labels = date_format("%b %Y")) + # format x axis
  theme(axis.text.x  = element_text(angle=45, vjust=0.5))  

ggplotly(p, tooltip = "text")
})
```


Women who screen positive {data-navmenu="Choose a view"}
=====================================

## Column {.sidebar}

Can describe page here, or include more control widgets

```{r}
hr()
min_date <-as.Date(min(Period)) # create min and max for slider
max_date <- as.Date(max(Period))

sliderInput("Date_range_selector5", "Date Range: ", min = min_date, max =max_date, value=as.Date(c("2018-01-01","2018-12-01")),timeFormat="%b %Y") # date slider
# each has a different title "Date_range_selectorN" ... be sure to change

hr()
```


## Row {.tabset .tabset-fade}

### Women who screened positive for depression
```{r}
renderPlotly({
p<-select(agg_maternal, c("PrenatalPctPos", "PostPctPos", "Period")) %>% 
  rename(., Prenatal = PrenatalPctPos, Postpartum = PostPctPos) %>% # rename variables
  gather(., key = timepoint, value = measure, "Prenatal", "Postpartum") %>% # reshape to plot
  filter(between(as.Date(Period),
                                      input$Date_range_selector5[1], 
                                      input$Date_range_selector5[2])) %>% 
  # each has a different title "Date_range_selectorN" ... be sure to change
  ggplot(., aes(y = measure, x = Period, 
              color = timepoint, # plot each timepoint a different color and line
              group = timepoint, 
              text = paste(round(measure,3)*100,"% screened", # tooltip text
                           "",timepoint,
                           "",
                           'month: ', paste(month(Period, label = TRUE),year(Period))))) +  
  geom_line(stat = "summary") + # plot lines
  geom_point(alpha = .5) + # points with transparency
  xlab("Month") + # axis labels
  ylab("Proportion Screened") +
  ggtitle("Women who screened positive for depression") + # plot title
  geom_hline(yintercept=.12, linetype="dashed", color = "black") + # reference line and label
  annotate(geom="text", label="12% positive screen rate for PRAMS", x = as.POSIXct('2018-03-01'), y=.121, vjust=-1) + 
  scale_x_datetime(date_breaks = "1 month", labels = date_format("%b %Y")) + # format x axis
  theme(axis.text.x  = element_text(angle=45, vjust=0.5)) + # x labels at 45 deg angle
  labs(color = "") # remove legend title

ggplotly(p, tooltip = "text")
})
```

### Screened positive, tables

```{r}
Z<-select(maternal, c("SiteName","PreM2Data_NUM","PreM2Data_DEN", "Period")) %>% # reshape data
  group_by(Period) %>% 
  filter(!is.na(PreM2Data_NUM)) %>% # don't sum over NA
  summarise("prenatal pos" = sum(PreM2Data_NUM), # row labels
            "denom" = sum(PreM2Data_DEN), 
            `n SiteName` = n()) 
new<-t(Z) # transpose df
Z$Period <- paste(month(Z$Period, label = TRUE),year(Z$Period)) %>% as.character() # column labels
colnames(new) <-Z$Period
new[-1,] %>% knitr::kable(caption = "Women who screened positive at their first prenatal visit") # pretty table with title

Z<-select(maternal, c("SiteName","PostM2Data_NUM","PostM2Data_DEN", "Period")) %>% # reshape data
  group_by(Period) %>% 
  filter(!is.na(PostM2Data_NUM)) %>% # don't sum over NA
  summarise("postpartum pos" = sum(PostM2Data_NUM), # row labels
            "denom" = sum(PostM2Data_DEN), 
            `n SiteName` = n()) 
new<-t(Z) # transpose df
Z$Period <- paste(month(Z$Period, label = TRUE),year(Z$Period)) %>% as.character()  # column labels
colnames(new) <-Z$Period
new[-1,] %>% knitr::kable(caption = "Women who screened positive at their postpartum visit") # pretty table with title
```

Connected to follow-up {data-navmenu="Choose a view" data-orientation=rows}
=====================================

## Column {.sidebar}

Can describe page here, or include more control widgets

```{r}
hr()
min_date <-as.Date(min(Period)) # create min and max for slider
max_date <- as.Date(max(Period))

sliderInput("Date_range_selector6", "Date Range: ", min = min_date, max =max_date, value=as.Date(c("2018-01-01","2018-12-01")),timeFormat="%b %Y") # date slider
# each has a different title "Date_range_selectorN" ... be sure to change

hr()
```


## graph {data-height=950}
### Women who screened positive connected to followup
```{r}
renderPlotly({
p<-select(agg_maternal, c("PrenatalPctConnected", "PostPctConnected", "Period")) %>%
  rename(., Prenatal = PrenatalPctConnected, Postpartum = PostPctConnected) %>% # rename variables
  gather(., key = timepoint, value = measure, "Prenatal", "Postpartum") %>%  # reshape to plot
  filter(between(as.Date(Period),
                                      input$Date_range_selector6[1], 
                                      input$Date_range_selector6[2])) %>% 
  # each has a different title "Date_range_selectorN" ... be sure to change
  ggplot(., aes(y = measure, x = Period, 
              color = timepoint, # plot each timepoint a different color and line
              group = timepoint, 
              text = paste(round(measure,3)*100,"% screened", # tooltip text
                           "",timepoint,
                           "",
                           'month: ', paste(month(Period, label = TRUE),year(Period))))) + 
  geom_line(stat = "summary") + # plot line
  geom_point(alpha = .5) + # points with transparency
  xlab("Month") + # axis labels
  ylab("Proportion Screened") +
  ggtitle("Women who screened positive connected to treatment/follow-up") + # plot title
  geom_hline(yintercept=1, linetype="dashed", color = "black") + # reference line and label
  annotate(geom="text", label="target 100%", x = as.POSIXct('2018-02-01'), y=.998, vjust=-1) +
  scale_x_datetime(date_breaks = "1 month", labels = date_format("%b %Y")) + # format x axis
  theme(axis.text.x  = element_text(angle=45, vjust=0.5)) + # x labels at 45 deg angle
  labs(color = "") # remove legend title

ggplotly(p, tooltip = "text")
})
```

## tables {.tabset .tabset-fade}
### Women who connected to follow-up/treatment after their first prenatal visit
```{r}
Z<-select(maternal, c("SiteName","PreM3Data_NUM","PreM3Data_DEN", "Period")) %>% # reshape data
  group_by(Period) %>% 
  filter(!is.na(PreM3Data_NUM)) %>% # don't sum over NA
  summarise("# referred" = sum(PreM3Data_NUM), # row labels
            denom = sum(PreM3Data_DEN), 
            `n SiteName` = n()) 
new<-t(Z) # transpose df
Z$Period <- paste(month(Z$Period, label = TRUE),year(Z$Period)) %>% as.character() # column labels
colnames(new) <-Z$Period
new[-1,] %>% knitr::kable(caption = "Women who connected to follow-up/treatment after their first prenatal visit") # pretty table with title
```

### Women who connected to follow-up/treatment after their postpartum visit
```{r}
Z<-select(maternal, c("SiteName","PostM3Data_NUM","PostM3Data_DEN", "Period")) %>% # reshape data
  group_by(Period) %>% 
  filter(!is.na(PostM3Data_NUM)) %>% # don't sum over NA
  summarise("# referred" = sum(PostM3Data_NUM), # row labels
            denom = sum(PostM3Data_DEN), 
            `n SiteName` = n()) 
new<-t(Z) # transpose df
Z$Period <- paste(month(Z$Period, label = TRUE),year(Z$Period)) %>% as.character() # column labels
colnames(new) <-Z$Period
new[-1,] %>% knitr::kable(caption = "Women who connected to follow-up/treatment after their postpartum visit") # pretty table with title
```


# Women positive and eligible {data-navmenu="Choose a view"}
=====================================

## Column {.sidebar}

Can describe page here, or include more control widgets

```{r}
hr()
min_date <-as.Date(min(Period)) # create min and max for slider
max_date <- as.Date(max(Period))

sliderInput("Date_range_selector7", "Date Range: ", min = min_date, max =max_date, value=as.Date(c("2018-01-01","2018-12-01")),timeFormat="%b %Y") # date slider
# each has a different title "Date_range_selectorN" ... be sure to change

hr()
```


## Graph
### Total women screened for maternal depression (out of number of eligible women)
```{r}
renderPlotly({
p<-select(agg_maternal, c("PreM1Data_DEN", "PreM2Data_NUM", "Period")) %>% 
  rename(., Eligible = PreM1Data_DEN, Positive = PreM2Data_NUM) %>% # rename variables
  gather(., key = status, value = measure, "Eligible", "Positive") %>% # reshape to plot
  filter(between(as.Date(Period),
                                      input$Date_range_selector7[1], 
                                      input$Date_range_selector7[2])) %>% 
  # each has a different title "Date_range_selectorN" ... be sure to change
  ggplot(., aes(y = measure, x = Period, 
              fill = status, # color by eligible or positive
              text = paste(round(measure,3),status, # tooltip text
                           "",
                           'month: ', paste(month(Period, label = TRUE),year(Period))))) + 
  geom_bar(stat = "summary", position = position_stack(reverse = TRUE)) + # make stacked bars
  xlab("Month")+ # axis labels
  ylab("Number Screened")+
  ggtitle("Total women screened for maternal depression (out of number of eligible women)") + # plot title
  scale_x_datetime(date_breaks = "1 month", labels = date_format("%b %Y")) + # format x axis
  theme(axis.text.x  = element_text(angle=45, vjust=0.5)) + # x labels at 45 deg angle
  labs(fill = "") # remove legend title

ggplotly(p, tooltip = "text")
})
```

Tutorial info {data-orientation=columns}
=====================================
I can change the orientation on new pages using `{data-orientation=columns}` etc

## make a column

### References 
```{r}
# more pages for more things!
```
#### flexdashboard

- flex dashboards can be static or made interactive by using `runtime: shiny`

[flex dashboard guide](https://rmarkdown.rstudio.com/flexdashboard/index.html)

[layout guide](https://rmarkdown.rstudio.com/flexdashboard/layouts.html#overview)

[dashboard chapter in markdown book](https://bookdown.org/yihui/rmarkdown/dashboards.html)

#### ggplot

[reference](https://ggplot2.tidyverse.org/reference/)

[tutorial from r-statistics](http://r-statistics.co/R-Tutorial.html)

#### plot.ly

- `plot.ly` creates interactive plots

- as seen on previous page, you can also wrap `ggplot` objects in `ggplotly` to make them interactive

[plot.ly guide](https://plot.ly/r)

[cheatsheet](https://images.plot.ly/plotly-documentation/images/r_cheat_sheet.pdf?_ga=2.221695057.832877277.1554941189-624079522.1510715632)

[ggplotly](https://plot.ly/ggplot2/user-guide/)

#### shiny app

- you can also make a shiny app, which uses more html - like syntax

[shiny guide: getting started](https://rstudio.github.io/shinydashboard/get_started.html)

[shiny guide: structure](https://rstudio.github.io/shinydashboard/structure.html#background-shiny-and-html)

[shiny tutorial from RStudio](http://shiny.rstudio.com/tutorial)

[another resource](https://docs.rstudio.com/shinyapps.io/)

## column 2

### another column

lets put some text in it

note you can use markdown syntax for headings as shown below:

- to make new column or row:

`## name` or 

`name`

`------------------------`

- `### title` makes the caption

- `####` will make headers
