---
title: "Dashboard Tutorial"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
runtime: shiny
---

```{r setup, include=FALSE}
library(flexdashboard)
library(dplyr)
library(tidyverse)
library(shiny)
library(ggplot2)
library(plotly)
```

```{r}
# make the mock data

set.seed(42)

site = c("A","B","C","D","E")
month = as.numeric(rep(1:12, each = 5))

df = as.data.frame(cbind(site,month))
df$site <- as.character(df$site)
df$month<-factor(df$month,levels(df$month)[c(1,5,6,7,8,9,10,11,12,2,3,4)])

df$n_eligible_prenatal = rep(floor(runif(12,100,500)), 5)
df$n_prenatal_screen = floor(df$n_eligible_prenatal*(runif(60,.45,.65)))
df$n_prenatal_pos = ceiling(df$n_prenatal_screen*(runif(60,.05,.15)))
df$n_followup_pre = ceiling(df$n_prenatal_pos*(runif(60,.9,1)))

#n_postpartum_screen = 
#n_eligible_postpartum = 
#n_postpartum_pos = 
#n_followup_post = 

attach(df)

df$Mpre.1 = n_prenatal_screen / n_eligible_prenatal
df$Mpre.2 = n_prenatal_pos / n_prenatal_screen
df$Mpre.3 = n_followup_pre / n_prenatal_pos

#Mpost.1 = n_postpartum_screen / n_eligible_postpartum
#Mpost.2 = n_postpartum_pos / n_postpartum_screen
#Mpost.3 = n_followup_post / n_postpartum_pos

maternal <- df

attach(maternal)
```

```{r}
# below I create page 1 with a sidebar for site selector and 4 plots, in 2 rows
# similar syntax can be used on other pages to create more dashboards
```


Page 1
=====================================

### Here is an example for the maternal data


Column {.sidebar}
-----------------------------------------------------------------------

```{r widget}
# select each site with drop down menus

hr()

which_site <- maternal %>% distinct(site) %>% pull %>% as.character() %>% sort()

selectInput("site_choice1", label = ("Select Site"),
            choices = which_site, selected = "A")
selectInput("site_choice2", label = ("Select Site"),
            choices = which_site, selected = "B")

selectInput("site_choice3", label = ("Select Site"),
            choices = which_site, selected = "C")

selectInput("site_choice4", label = ("Select Site"),
            choices = which_site, selected = "D")

# slider for date range can go here
# sliderInput('sampleSize', 'Sample Size', min=1, max=nrow(dataset),
#             value=min(1000, nrow(dataset)), step=500, round=0)
```

You can put text in the sidebar like this!

Row 1
-----------------------------------------------------------------------

### plot 1 (this is where you put the title)
```{r, eval = F}

renderPlotly({                                                        # render the interactive plot

  # create a ggplot and make interactive by calling ggplotly
  # if you don't want interactivity, use renderPlot({ }) and don't wrap with ggplotly
  
p<- maternal %>% filter(site == input$site_choice1) %>%               # filters only the site the user chose
    ggplot(aes(x=month, y=Mpre.2, group= 1,                           # group = 1 to plot since each month has 1 data point
               text = paste('site: ', site, "<br>",                   # create tooltip text
                            'proportion positive: ', Mpre.2))) +
      geom_line(aes(x=month, y=Mpre.2),color = "red") +               # each panel has its own color
      geom_point() +                                                  # show the points
      geom_hline(yintercept=0.12, linetype="dashed", color = "black") + # horizontal reference line
      xlab("Month")+
      ylab("Proportion")

ggplotly(p, tooltip = ("text"))
  })
```

```{r}
# syntax for plotly
renderPlotly({
  
maternal %>% filter(site == input$site_choice1) %>% # filters only the site the user chose
    plot_ly(x = ~month, y = ~Mpre.2
          , color = I('red')                        # set color of line
          , type = "scatter", mode = "lines+markers"# line plot with dot markers
          , alpha = 0.5                             # size control
          , hoverinfo = 'text'                      # set hover text
          , text = ~paste("site: ", site, '\nproportion: ', round(Mpre.2,2))
            ) %>% 
    add_lines(x=c(0,12), y=c(.12,.12)               # create gray reference line
              , color = I('gray')
              , hoverinfo = 'text'                  # hover text
              , text = ~paste("12% PRAMS")) %>% 
              layout(showlegend = F) %>%            # no legend 
    layout(xaxis=list(title = "month")              # set axis titles
           , yaxis=list(title = "proportion"))
  })

```

### plot 2

```{r, eval = T}

renderPlotly({


p2<-maternal %>% filter(site == input$site_choice2) %>%
  ggplot(aes(x=month, y=Mpre.2, group= 1, 
               text = paste('site: ', site, "<br>",
                            'proportion positive: ', Mpre.2))) +
      geom_line(aes(x=month, y=Mpre.2),color = "blue") +
      geom_point() +
      geom_hline(yintercept=0.12, linetype="dashed", color = "black") + 
      xlab("Month")+
      ylab("Proportion")

ggplotly(p2, tooltip = c("text"))
  })

```

Row 2
-----------------------------------------------------------------------
###plot 3
```{r}
renderPlotly({


p3<-maternal %>% filter(site == input$site_choice3) %>%
    ggplot(aes(x=month, y=Mpre.2, group= 1, 
               text = paste('site: ', site, "<br>",
                            'proportion positive: ', Mpre.2))) +
      geom_line(aes(x=month, y=Mpre.2),color = "dark green") +
      geom_point() +
      geom_hline(yintercept=0.12, linetype="dashed", color = "black") + 
      xlab("Month")+
      ylab("Proportion")

ggplotly(p3, tooltip = c("text"))
})

```

###plot 4
```{r}
renderPlotly({


p4<-maternal %>% filter(site == input$site_choice4) %>%
    ggplot(aes(x=month, y=Mpre.2, group= 1,    
               text = paste('site: ', site, "<br>",
                            'proportion positive: ', Mpre.2))) +
      geom_line(aes(x=month, y=Mpre.2),color = "purple") +
      geom_point() +
      geom_hline(yintercept=0.12, linetype="dashed", color = "black") + 
      xlab("Month")+
      ylab("Proportion")

ggplotly(p4, tooltip = c("text"))
})

```

Page 2 {data-orientation=columns}
=====================================

I can change the orientation on new pages using `{data-orientation=columns}` etc

## make a column

### References 

```{r}
# more pages for more things!
```

#### flexdashboard

- flex dashboards can be static or made interactive by using `runtime: shiny`

[flex dashboard guide](https://rmarkdown.rstudio.com/flexdashboard/index.html)

[layout guide](https://rmarkdown.rstudio.com/flexdashboard/layouts.html#overview)

[dashboard chapter in markdown book](https://bookdown.org/yihui/rmarkdown/dashboards.html)

#### ggplot

[reference](https://ggplot2.tidyverse.org/reference/)

[tutorial from r-statistics](http://r-statistics.co/R-Tutorial.html)

#### plot.ly

- `plot.ly` creates interactive plots
- as seen on previous page, you can also wrap `ggplot` objects in `ggplotly` to make them interactive

[plot.ly guide](https://plot.ly/r)

[cheatsheet](https://images.plot.ly/plotly-documentation/images/r_cheat_sheet.pdf?_ga=2.221695057.832877277.1554941189-624079522.1510715632)

[ggplotly](https://plot.ly/ggplot2/user-guide/)

#### shiny app

- you can also make a shiny app, which uses more html - like syntax

[shiny guide: getting started](https://rstudio.github.io/shinydashboard/get_started.html)
[shiny guide: structure](https://rstudio.github.io/shinydashboard/structure.html#background-shiny-and-html)

[shiny tutorial from RStudio](http://shiny.rstudio.com/tutorial)

[another resource](https://docs.rstudio.com/shinyapps.io/)

## column 2

### another column

lets put some text in it


note you can use markdown syntax for headings as shown below:

- to make new column or row:

`## name` or 

`name`

`------------------------`


- `### title` makes the caption

- `####` will make headers


Page 3
=====================================

## row

### here's a row

## Row {.tabset .tabset-fade}

### chart 1

this is a tabbed view!

### chart 2













